MSstatsPTM statistical relative quantification of post-translational modifications in global proteomics experiments \textbf{Supplementary Information}

### 2022-07-28 supplementary/ptm_sm.tex
added ref to supp

We compared six different approaches as follows: a) proposed approach, b) proposed approach without adjusting for unmodified peptides c) ANOVA (with adjustment), d) ANOVA (no adjustment), e) Limma (with adjustment), and f) Limma (no adjustment).

@@

\clearpage
\subsubsection{Dataset 5 : Mouse - Phosphorylation - 2mix-TMT}
\label{sec:shigella}

@@

\subsubsection{Dataset 6 : Human - Ubiquitination - Label-free no global profiling run}
\label{sec:usp30}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage

%\printbibliography

>>>>

We compared six different approaches as follows: a) proposed approach, b) proposed approach without adjusting for unmodified peptides c) ANOVA~\cite{kutner_etal_04a} (with adjustment), d) ANOVA (no adjustment), e) Limma~\cite{Smyth:2004} (with adjustment), and f) Limma (no adjustment).

@@

\clearpage
\subsubsection{Dataset 5 : Mouse - Phosphorylation - 2mix-TMT~\cite{Maculins}}
\label{sec:shigella}

@@

\subsubsection{Dataset 6 : Human - Ubiquitination - Label-free no global profiling run~\cite{Cunningham2015}}
\label{sec:usp30}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage

\printbibliography
